Put Title here

### 2018-06-12 General WLD combinatorics.tex
some typos fixed

\begin{dfn}
Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex. For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ (or $w \in \{i+1, j+1\}$)a vertex of $W$, let $P_{v}$ (or $P_w$) to be a \emph{protecting set of $p$ at $v$ (or $w$) at $a$} be a set of up to $3$ propagators defined as follows: \begin{enumerate}
\item Work under the linear order on $[n]$, $<_{v+1}$ or $<_w$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$. 
\item There is a propagator $s_1 \in P_v$ and $s_4 \in P_w$ defined such that $s_4 = (i_{s_4}, v)$ and $s_1 = (i_{s_1}, v)$. One may also have $s_1 = (i_{s_1}, v-1)$. Furthermore, $s_m \in [i_p, v]$.
\item For the given $a$, either $a-3 <_{v+1} i_{s_1}$ or there exist $2$ propagators $s_2$ and $s_3 \in P_v$ such that $s_3 = (i_{s_3}, i_{s_1})$ and $s_2 = (i_{s_2}, i_{s_1})$. One may also have $s_2 = (i_{s_2}, i_{s_1}-1)$. Furthermore, $a-3 <_{v+1} s_m$. Similarly, for the given $a$, either $a-3 <_{v+1} i_{s_4}$ or there exist $2$ propagators $s_5$ and $s_6 \in P_w$ such that $s_5 = (i_{s_5}, i_{s_4})$ and $s_6 = (i_{s_6}, i_{s_4})$. One may also have $s_6 = (i_{s_6}, i_{s_4}-1)$. Furthermore, $a-3 <_w s_m$.
\end{enumerate}
\end{dfn}

\begin{comment}
\begin{dfn}
Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex. For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ (or $w \in \{i+1, j+1\}$) an edge of $W$, let $P_{v}$ (or $P_w$) to be a \emph{protecting set of $p$ at $v$ (or $w$) at $a$} defined as follows: \begin{enumerate}
\item Work under the linear order on $[n]$, $<_{v+1}$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$. 
\item The sets $P_v$ and $P_w$ are disjoint. 
\item There is an $r \in P_{v}$ such that $j_r \in \{v, v-1\}$ and $ i_r \in [i_p, j_p]$. If $j_r = v-1$, then $r$ is the clockwise most propagator on the edge $v$. Similarly, there is a $r \in P_{w}$ such that $j_r =v$ and $ i_r \in [i_p, j_p]$.
\item For every $q = (i_q, j_q) \in P_{v}$, or $P_w$, if there are at least two propatagors $s$ and $t$ $\in \cP$ satisfying $s = (i_s, i_q)$ or $s = (i_s, i_q-1 )$ (in which case $s$ is the clockwise most propagator on the edge $i_q$) and $t = (i_t, i_t)$ then all such $s$ and $t$ are also in $P_v$ or $P_w$. These are called the daughter propagators of $q$. If two such propagators don't exist, then $q$ is called a terminal propagator. 
\item For the $a$ given above, there is a propagator $q$ with a set of daughters $\{s_m\}$ satisfying $a-3 <_{v+1} i_{s_m}$.
\end{enumerate} 
\end{dfn}
\end{comment}

@@

\begin{comment}
\begin{lem}\label{protecting lem}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$. Then $p$ does not contribute $i$ or $j$ to $I_a$ if there is a subtree protecting $i$ or $j$ from $a$ in $\tau(W)$. Furthermore, $p$ does not contribute $i+1$ or $j+1$ if there are two protecting subtrees, at least one of which has a leaf vertex at $v$.
\end{lem}

\begin{proof}
It is sufficient to prove this for $i$ and $i+1$. The other two can be proved by switching the roles of $i$ and $j$. We show this by contradiction.

Assume that $p$ does not contribute $i$ to $I_a$. Furthermore, that there is a binary tree $T$ protecting $p$ at $i$ from $a$. Then, there is some propagator $q= (i_q, j_q) \in \cP$ corresponding to a leaf of $T$ such that $i_q \in \{i, i-1\}$ and $j +1 \leq_j j_q \leq_j i$. Further, there are two propagators, $s_1 = (i_{s_1}, j_{s_1})$ and $t_1 = (i_{t_1}, j_{t_1})$ that contribute $i_q$ and $i_q +1$ respectively to $I_v$. Namely, we write \bas j \leq_j i_{t_1} <_j i_{s_1} <_j j_{s_1} \leq_j j_{t_1} = i_q\;,\eas with $j_{s_1} \in \{i_q, i_q-1\}$.

In order for $i_{s_1}$ and $i_{t_1}$ to respectively contribute $i_q$ and $i_q +1$, there must be $4$ other propagators, $i_{s_2}$, $i_{t_2}$, $i_{s_3}$, and $i_{t_3}$ that contribute $i_{s_1}$, $i_{s_1}+1$, $i_{t_1}$ and $i_{t_1}+1$ respectively.

For each $s_m$ and $t_m$ thus identified, t here must be other pairs of propagators, $s_{m'}$ and $s_{m'}$ (with $m'> m$) that are removed at steps $i_{s_m}$ and $i_{s_m} +1$ or $i_{t_m}$ and $i_{t_m}+1$. Note that under this construction, $i_{t_m} <_j i_{s_m}$. By construction, each of these propagators must have endpoints in $[a,i] \cap [j,i]$.

There are now three cases to be considered. Let $p_k$ indicate a propagator identified at an earlier stage of this construction (that is, $ m\geq k > 0$ and $p_k \in \{s_k, t_k\}$, or $p_k$ is the first propagator of $T$ lying counterclockwise from $a$.).

 \begin{description}
\item[$i_{t_m} = i_{p_k}+2$] Then there is not room to place both the propagators $s_{m'}$, and $t_{m'}$. Thus $t_m$ is removed at the step $i_{t_m} + 1$. Therefore, $q$ contributes at either $i_q$ or $i_q+1$.
 \item[$i_{t_m} = i_{p_k}+1$] Then there is not room to place either the propagators $s_{m'}$, and $t_{m'}$. Thus $t_m$ is removed at the step $i_{t_m}$. Therefore, $q$ contributes at either $i_{a}$ or $j_{q}+1$.
 \item[$i_{t_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$. Therefore consider the propagators that ensure that $s_m$ is not removed at $i_{s_m}$ or $i_{s_m}+1$. By the above argument, there exists an $t_{m'}$ such that $i_{t_m'} = i_{t_m}$. This requires the existence of propagators such that $s_m'$ is not removed at $i_{s_m'}$ or $i_{s_m'}+1$. This argument continues at infinitum, contradicting both the fact that there are only a finite number of propagators in $W$, and that at most $i_{s_m} - i_{t_m}-1$ propagators can be supported on the cyclic interval $\{i_{t_m}, i_{s_m}+1\}$.
 \end{description}

Since all of these cases lead to a contradiction, one cannot both have $p$ not contribute $j$ to $I_a$ and not have a binary tree $T$ protecting $p$ at $j$ from $a$.

The argument for $j+1$ is the same with two trees, $T_1$ and $T_2$, one leaf of $T_1$ preventing $p$ from contributing $j$ to $I_a$, and the corresponding leaf of $T_2$ preventing $p$ from contributing $j+1$.

@@

\begin{comment}

\begin{lem}\label{useful lem for GN alg}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i, j) \in \cP$. Let $v$ be a vertex such that $i +1 \leq_i v \leq_i j$ (resp. $j +1 \leq_j v \leq_j i$). If there exists another propagator $q = (i_q, j_q)$ such that $i_q \in \{i, i-1\}$ and $j +1 \leq_j j_q \leq_j i$, (resp. $j_q \in \{j, j-1\}$ and $i +1 \leq_i i_q \leq_i j$), then $q$ contributes $m_v$ to $I_v$, where $m_v \in \{j, j+1\}$, (resp. $m_v \in \{i, i+1\}$).
\end{lem}

\begin{proof}
In this proof, we consider the case where $i +1 \leq_i v \leq_i j$. The situation when $j +1 \leq_j v \leq_j i$ is similarly proved by exchanging the roles of $i$ and $j$.

Suppose the statement doesn't hold. Then, for some propagator $q= (i_q, j_q) \in \cP$ such that $i_q \in \{i, i+1\}$ and $j +1 \leq_j j_q \leq_j i$, there are two propagators, $s_1 = (i_{s_1}, j_{s_1})$ and $t_1 = (i_{t_1}, j_{t_1})$ that contribute $i_q$ and $i_q +1$ respectively to $I_v$. Namely, we write \bas j \leq_j i_{t_1} <_j i_{s_1} <_j j_{s_1} \leq_j j_{t_1} = i_q\;,\eas with $j_{s_1} \in \{i_q, i_q-1\}$.

In order for $i_{s_1}$ and $i_{t_1}$ to respectively contribute $i_q$ and $i_q +1$, there must be $4$ other propagators, $i_{s_2}$, $i_{t_2}$, $i_{s_3}$, and $i_{t_3}$ that contribute $i_{s_1}$, $i_{s_1}+1$, $i_{t_1}$ and $i_{t_1}+1$ respectively.

For each $s_m$ and $t_m$ thus identified, t here must be other pairs of propagators, $s_{m'}$ and $s_{m'}$ (with $m'> m$) that are removed at steps $i_{s_m}$ and $i_{s_m} +1$ or $i_{t_m}$ and $i_{t_m}+1$. Note that under this construction, $i_{t_m} <_j i_{s_m}$.

There are now three cases to be considered. Let $p_k$ indicate a propagator identified at an earlier stage of this construction (that is, $ m\geq k > 0$ and $p_k \in \{s_k, t_k\}$, or $p_k = p$).

 \begin{description}
\item[$i_{t_m} = i_{p_k}+2$] Then there is not room to place both the propagators $s_{m'}$, and $t_{m'}$. Thus $t_m$ is removed at the step $i_{t_m} + 1$. Therefore, $q$ contributes at either $i_q$ or $i_q+1$.
 \item[$i_{t_m} = i_{p_k}+1$] Then there is not room to place either the propagators $s_{m'}$, and $t_{m'}$. Thus $t_m$ is removed at the step $i_{t_m}$. Therefore, $q$ contributes at either $i_{a}$ or $j_{q}+1$.
 \item[$i_{t_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$. Therefore consider the propagators that ensure that $s_m$ is not removed at $i_{s_m}$ or $i_{s_m}+1$. By the above argument, there exists an $t_{m'}$ such that $i_{t_m'} = i_{t_m}$. This requires the existence of propagators such that $s_m'$ is not removed at $i_{s_m'}$ or $i_{s_m'}+1$. This argument continues at infinitum, contradicting both the fact that there are only a finite number of propagators in $W$, and that at most $i_{s_m} - i_{t_m}-1$ propagators can be supported on the cyclic interval $\{i_{t_m}, i_{s_m}+1\}$.
 \end{description}

\begin{cor} \label{useful cor for GN alg}
The above lemma also holds for $v = j+1$ (resp. $v = i+1$, unless $q = (i-1, j)$ (resp. $q = (j-1, i)$).
\end{cor}
\begin{proof}
The proof is exactly as above. This statement is not included in the statement of the previous lemma only out of concerns for linguistic clarity.
\end{proof}
\end{comment}

>>>>

\begin{dfn}\label{protect dfn}
Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex. For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ (or $w \in \{i+1, j+1\}$)a vertex of $W$, let $P_{v}$ (or $P_w$) to be a \emph{protecting set of $p$ at $v$ (or $w$) at $a$} be a set of up to $3$ propagators defined as follows: \begin{enumerate}
\item Work under the linear order on $[n]$, $<_{v+1}$ or $<_w$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$.
\item There is a propagator $s_1 \in P_v$ and $s_4 \in P_w$ defined such that $s_4 = (i_{s_4}, v)$ and $s_1 = (i_{s_1}, v)$. One may also have $s_1 = (i_{s_1}, v-1)$. Furthermore, $s_m \in [i_p, v]$.
\item For the given $a$, either $a-3 <_{v+1} i_{s_1}$ or there exist $2$ propagators $s_2$ and $s_3 \in P_v$ such that $s_3 = (i_{s_3}, i_{s_1})$ and $s_2 = (i_{s_2}, i_{s_1})$. One may also have $s_2 = (i_{s_2}, i_{s_1}-1)$. Furthermore, $a-3 <_{v+1} s_m$.\end{enumerate}
\end{dfn}

@@

@@
